### 2013-12-17 poster_new/conference_poster_4.tex
new design for poster - more formatting

\documentclass[portrait,a1paper,fontscale=0.5]{baposter} % Adjust the font scale/size here

@@

\headerbox{METRICS}{name=metrics,column=1,span=2,row=2,below=solution}{
\begin{itemize}
\item Path length (number of hops) of the routes assigned to flows.
\item Maximum link utilization of the path assigned to flows.
\item Communication overhead (number of messages exchanged between controllers) for setting up routes for flows.   
\end{itemize}

\begin{center}
\includegraphics[scale=0.3]{msg}
\captionof{figure}{Per flow communication overhead}
\label{fig:msg}
\end{center}

\begin{minipage}{.5\textwidth}
\begin{center}
\includegraphics[scale=0.3]{path.png}
\captionof{figure}{Path length}
\label{fig:path}
\end{center}
\end{minipage}

\begin{minipage}{.5\textwidth}
\begin{center}
\includegraphics[scale=0.3]{util.png}
\captionof{figure}{Maximum link utilization}
\label{fig:util}
\end{center}
\end{minipage}

@@

\headerbox{RESULTS}{name=results,column=0,row=3,below=exp}{

@@

\headerbox{RESOURCES}{name=resources,column=0,span=1,row=3,below=results}{

>>>>

\documentclass[portrait,a1paper,fontscale=0.45]{baposter} % Adjust the font scale/size here

@@

\headerbox{METRICS}{name=metrics,column=0,span=3,row=2,below=solution}{
\begin{itemize}
\item Path length (number of hops) of the routes assigned to flows.
\item Maximum link utilization of the path assigned to flows.
\item Communication overhead (number of messages exchanged between controllers) for setting up routes for flows.   
\end{itemize}
\begin{multicols}{3}
\begin{center}
\includegraphics[scale=0.3]{msg}
\captionof{figure}{Per flow communication overhead}
\label{fig:msg}
\end{center}

\begin{minipage}{.3\textwidth}
\begin{center}
\includegraphics[scale=0.3]{path.png}
\captionof{figure}{Path length}
\label{fig:path}
\end{center}
\end{minipage}

\begin{minipage}{.3\textwidth}
\begin{center}
\includegraphics[scale=0.3]{util.png}
\captionof{figure}{Maximum link utilization}
\label{fig:util}
\end{center}
\end{minipage}
\end{multicols}

@@

\headerbox{RESULTS}{name=results,column=0,span=2,row=3,below=metrics}{

@@

\headerbox{RESOURCES}{name=resources,column=2,span=1,row=3,below=metrics}{
